{ \centering Scientific Report - Summary of Research\\ ~\\ Automatized compilation of sequential software to a diverse set of hardware accelerators\\ } ~\\ \vspace{18em} \large Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
Report
Scientific report

@@

@@

@@

>>>>

Compared to the original proposal we continued to focus on LLVM/MLIR as an
infrastructure instead of Julia and not only used it to bring our ideas closer
to production compilers but indeed contributed many of our ideas directly into
a widely used software stack.

@@

01.02.2020 - Hiring of Christoph Mueller\\
01.11.2019 - Hiring of Tobias Gysi

@@

Tobias Grosser was leading the overall research agenda and lead the development
of our novel polyhedral core library. Tobias Gysi and Christoph Mueller have
been pivotal to the development of the climate DSL and the GPU backend that we
developed. They did not only contribute to the scientific ideas, but
contributed high-quality code to the LLVM/MLIR framework directly. As a result,
they got hired by MeteoSwiss and Google right after the termination of this
project. Theodoris Theodoridis contributed significantly to both the polyhedral
math library as well as the inlining model we developed. Tobias Gysi was also
pivotal in supporting most other work on the LLVM/MLIR side that took place via
interns and researchers hired via our industrial funding. In particular, in
2019 visitors played a pivotal role: (1) Arjun Pitchanathan as contributor
to our fast simplex and the fast Presburger library we built on top, (2)
Mathieu Fehr as contributor to our declarative compilation work, (3) Lorenzo
Chelini as a long-term visiting researcher contributing to pattern recognition
and our declarative compilation infrastructure, (4) Asif Ali Kahn on applying
our polyhedral tools to racetrack memory.

@@

In the third part of this project, we published eight papers (seven peer
reviewed) and have six additional papers currently under review.
